\documentclass[12pt]{scrartcl}
\usepackage{soul}% for the underlining 

\usepackage{emerald}% for 1-4
\usepackage[T1]{fontenc}

%opening
\author{Anton Kaminsky \and Jeffrey Li \and Christian Sarran \and Kelvin Duong \and Zifan Gao}
\title{D\'evlopp Team Expectations Agreement}

\begin{document}
\maketitle

\section{Method of communication}
We will be using Slack for nearly all team communications because we can easily post links, pictures and otherwise communication, and organize our discussions on different threads. We will also use Facebook messenger, for quick on the go messages, like checking in on someone, so we are not cluttering our Slack channel. 

\subsection{Response time}
Our goal for response time is 4 hours. In the worst case, the response time is to be no longer than 24 hours.

\section{Team meetings}
We will run mandatory weekly face-to-face meetings on Wednesday at 1pm in the IC Lab. If this time is not suitable for all team members, our backup time is Monday at 6pm. If we need more meeting times we will discuss as needed. Anton will take the minutes and post upload them to the GitHub repo. Everyone is expected to participate in these meetings.

\subsection{Meeting prep}
We will confirm our meeting day and time by 6pm on Saturday in Slack, and figure out any topics or points to be discussed in the meetings. Christian will make a meeting outline from this discussion to ensure everyone knows what the meeting is for, so that we can stay on task.

\section{Version control}
Pushing code directly to the master branch of the project repo is prohibited. Members will branch and submit pull requests to the main repository on GitHub. This is called the shared repository model with branching. Each pull request must be reviewed by at least two other members before being merged into the main branch. Once a review has been completed, the member that made the pull request merges it in. No superfluous files should be committed to the repo. A \texttt{.gitignore} file will be used to make sure those files don't ever get staged or committed. Pull requests and commits must have meaningful and descriptive messages that summarize the changes made.

\section{Division of work}
We will divide work during the standard meeting times. Division should be as fair as possible and take into consideration the skills and abilities of the team members. We will take care to make sure that everyone is comfortable with the division before it is finalized.

\section{Submitting work}
Submissions will be reviewed by all team members and discussed on Slack before being submitted. Deliverables should be completed at least 24 hours before the submission deadline. Christian and Anton will be responsible for the final submission.

\section{Contingency planning}
If an issue with a team member affects our ability to work effectively for more than a week (e.g. missing meetings, being sick, etc.), we will have a discussion with them about the issue. If we are unable to resolve the issue internally within a day, we will reach out to our TA. Any action that violates the University's Code of Conduct will not be tolerated, and will immediately be reported to our TA.

\section{Quality of work}
Consistent coding style for all team-mates is a must. Documentation and comments must be detailed enough so that there are no questions about any parts of the implementation. Standard practices for documentation of APIs will be used for each language e.g. Java/Python. Good test coverage is enforced for all code written. Unit tests and Integration tests will be written for any code in the code base.

\section{Client meetings}
Meet the client if there are questions about the requirements of the project. There will be a text file in the repo that holds the questions that we want answered or have already answered. We will agree as a team when it is appropriate to meet the client and will immediately update our question log with the answers given by the client.

\section{TA meetings}
Prepare in advance with an overview of the work done and what still needs to be done. We will discuss any concerns we have with the TA and show them a quick demo of our product. Everyone is expected to be present, prepared and participating.

\section{Signatures}
{\Large {\ECFJD\setul{0.1ex}{}\ul{~~Anton Kaminsky~~}}}\\
{\Large {\ECFJD\setul{0.1ex}{}\ul{~~Jeffrey Li~~}}}\\
{\Large {\ECFJD\setul{0.1ex}{}\ul{~~Christian Sarran~~}}}\\
{\Large {\ECFJD\setul{0.1ex}{}\ul{~~Kelvin Duong~~}}}\\
{\Large {\ECFJD\setul{0.1ex}{}\ul{~~Zifan Gao~~}}}\\ 	

\end{document}
